---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wrappedgithubactivityapi)
```

The `wrappedgithubactivityapi` package wrapped a part of the [GitHub Activity APIs](https://docs.github.com/en/rest/reference/activity) for helping user to retrieve public / repository network / organization / repository events (activities). The package also provided some analysis conveniences by its statistical functionality and plot functionality.

In order to balance its flexibility and convenience, functions are designed to "3 levels".

## 1st Level - Data Retrieve Functions

User can use these functions to get all the information in the response with a user selected format, and make further analysis. These functions for providing the flexibility to user.

### Get Public Events

The `github_get_public_events` function will retrieve public events data and return the data in user selected format.

For example, user can retrieve the first page of public events with 10 event records per page:


```{r, results='hide'}
github_get_public_events(per_page=10, page=1)
```

The output is hidden, because the each public event record may contain too many key-value pairs to display. 

User can use the optional parameter `output_type` to indicate output formatting type (Possible value: "list","dataframe","character","raw") (default: "list").


### Get Organization Events

The `github_get_organization_events` function will retrieve organization events data and return the data in user selected format.

For example, user can retrieve the first page of organization events with 1 events records per page in "dataframe" output format:


```{r}
github_get_organization_events("ubco-mds-2021",1,1,output_type = "dataframe")
```

User can use the optional parameter `output_type` to indicate output formatting type (Possible value: "list","dataframe","character","raw") (default: "list").



### Get Repository Network Events

The `github_get_network_events` function will retrieve repository network events data and return the data in user selected format.

For example, user can retrieve the first page of repository network events with 1 events records per page in "dataframe" output format:


```{r}
github_get_network_events("AndrewNg1891","DATA534_API_Project_Group9",per_page=1,page=1,output_type = "character")
```

User can use the optional parameter `output_type` to indicate output formatting type (Possible value: "list","dataframe","character","raw") (default: "list").



### Get Repository Events

The `github_get_repo_events` function will retrieve repository events data and return the data in user selected format.

For example, user can retrieve the first page of repository events with 1 events records per page in "dataframe" output format:


```{r}
github_get_repo_events("AndrewNg1891","DATA534_API_Project_Group9",per_page=1,page=1,output_type = "dataframe")
```

User can use the optional parameter `output_type` to indicate output formatting type (Possible value: "list","dataframe","character","raw") (default: "list").


## 2nd Level - Data Select Function

The function in this part wrapped functions in the 1st level, and can handle the paginate problem for user. User can use this function to get last n events data without worry about how many records per page and which page to retrieve.

This function for providing some convenience to user.

### Get last n events

The `github_lastn_events_df` function will retrieve last n events data of a certain range (Possible value: "all public"/"network"/"organization"/"repository") and return the dataframe that contains the retrieved events data.of a certain range . The information in the response was selected on 5 most important things. 


For example, user can retrieve the last 15 events from organization "ubco-mds-2021":


```{r}
github_lastn_events_df("organization",15,organization="ubco-mds-2021")
```

For another example, user can retrieve the last 5 events from repository "DATA534_API_Project_Group9" with its owner name "AndrewNg1891":


```{r}
github_lastn_events_df("repository",15,owner="AndrewNg1891",repo="DATA534_API_Project_Group9")
```

## 3rd Level - Data Analysis Function

Functions in this part wrapped the function in the 2nd level, and preform some analysis for user. User can use these function to count and/or plot last n events data with a certain group condition.

These functions for providing some convenience to user.

### Count Events by Type

The `github_count_events_bytype` function will count the number of events by type for a certain range.


For example, user can count the number of events by type on last 20 events from repository "DATA534_API_Project_Group9" with its owner name "AndrewNg1891":


```{r}
github_count_events_bytype("repository",20,"AndrewNg1891","DATA534_API_Project_Group9")
```

### Count Events by Date

The `github_count_events_bydate` function will count the number of events by date for a certain range and type.


For example, user can count the number of "WatchEvent" type events by date on last 100 events from repository "WestHealth" with its owner name "pyvis":


```{r}
github_count_events_bydate("repository",100,"WestHealth","pyvis",event_type = "WatchEvent")
```


This function also provides visualization ability. For getting the plot, just need to set parameter `return_type = "plot"`, then the function will plot a bar chart base on the counted events data:

```{r}
github_count_events_bydate("repository",100,"WestHealth","pyvis",event_type = "WatchEvent",return_type = "plot")
```


### Count Events by Weekday

The `github_count_events_byweekday` function will count the number of events by weekdays for a certain range and type.


For example, user can count the number of events by date on last 100 events from repository "WestHealth" with its owner name "pyvis":


```{r}
github_count_events_byweekday("repository",100,"WestHealth","pyvis")
```


This function also provides visualization ability. For getting the plot, just need to set parameter `return_type = "plot"`, then the function will plot a bar chart base on the counted events data:

```{r}
github_count_events_byweekday("repository",100,"WestHealth","pyvis",return_type = "plot")
```


## Note - Rate Limit

The GitHub has rate limit on its activity API, which allows only 60 requests for unauthenticated user. However, this limit can be increased to 5000 for authenticated user. 

All functions in this package allows user input optional parameters `username` and `token` for authentication. 

The function `api_rate_limit` can be used to get rate limit information:


```{r}
api_rate_limit()
```







